\Title

### 2023-06-01 Grimaldi-etal-BiolCybernetics.tex
methods

To train and test our model, we need to define a visual dataset for which we control the direction and speed of motion. Let us now define a procedure for animating a natural visual scene with virtual eye movements, similar to those used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. First, we draw a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful because it allows the area with the highest density of photoreceptors in the environment to be moved, for example, to a point of interest. A specific mechanism for this function are saccades, which are rapid eye movements that reposition the center of vision. In humans, saccades are very frequent (on average $2$ per second~\citep{dandekar_neural_2012}). They are generated very quickly (about $80~\ms$) and have a wide range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological movements, we simplified it by selecting a set of eye movements as the Cartesian product of $8$ linearly spaced movement directions and 3 geometrically spaced speeds. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $24~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently of the set of different motion sets, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-\textit{(Left)}).

>>>>

To train and test our model, we need to define a visual dataset for which we supervise the direction and speed of motion. For this, we define a procedure for animating a natural visual scene with virtual eye movements, similar to those used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. First, we draw a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful because it allows the area with the highest density of photoreceptors in the environment to be moved, for example, to a point of interest. A specific mechanism for this function are saccades, which are rapid eye movements that reposition the center of vision. In humans, saccades are very frequent (on average $2$ per second~\citep{dandekar_neural_2012}), they are generated very quickly (about $80~\ms$) and have a wide range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological movements, we simplified it by selecting a set of eye movements as the Cartesian product of $XXX8$ linearly spaced movement directions and $XXX3$ geometrically spaced speeds. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $24~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently from the set of different motions, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-\textit{(Left)}).
